Figure 3b

### 2018-05-16 inst/supp_figure4b/supp_fig4b.Rmd
adding supp fig 4b

@@

>>>>

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

_Representative result_

```{r, out.width = "850px"}

url <- fileMap(type = "png")["Supplementary Figure 4b"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

<div class = "caption">
Representative flow cytometry analysis from the cell cycle analysis in Figure 3B.
</div>
